A star formation event in the leading arm of the Magellanic stream triggered by passage through the outer Galactic disk

### 2018-07-21 ms.tex
updates

% typography
\setlength{\parindent}{1.\baselineskip}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\package}[1]{\textsl{#1}}
\newcommand{\gaia}{\textsl{Gaia}}
\newcommand{\pans}{\textsl{Pan-STARRS}}
\newcommand{\DR}[1]{\acronym{DR#1}}
\newcommand{\todo}[1]{{\color{red} TODO: #1}}

@@

\section{Data and cluster discovery} \label{sec:data}

@@

We then query all objects from the \gaia\ \DR{2} catalog within a polygon centered on the nominal position of the group (see above), with a width of $12^\circ$ and a height of $8^\circ$ in the Magellanic stream coordinate system \citep{Nidever:2008} (see Appendix~\ref{sec:queries} for the database query).
We cross-match the resulting catalog with \acronym{GALEX} \todo{citation} using a positional crossmatch requiring source separation $<2~\textrm{arcsec}$, and with \acronym{PS1} \todo{citation}\citep{Chambers:XX} using the cross-match provided by the \gaia\ science archive.
\figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram (left) and the \acronym{GALEX} NUV minus \acronym{PS1} $g$-band vs. \gaia\ \bprp\ color-color diagram (right) from the cross-matched photometry.
All magnitudes are corrected for dust extinction using the SFD \citep{Schlegel:1998} dust map.
The green polygon in the left panel of \figurename~\ref{fig:cmds} highlights the over-density of blue stars that were identified as comoving from the proper motion search described above.
The red line in right panel of \figurename~\ref{fig:cmds} is an isochrone (from MIST; \citealt{TODO}) for a $50~\textrm{Myr}$, $\feh = -1$ stellar population.

% Notebook: Figure-CMDs
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/gaia-galex-cmd.pdf}
\caption{Color-magnitude and color-color diagrams with \gaia\ ($G$, BP, RP), \acronym{GALEX} (NUV), and \acronym{PS1} ($g$) magnitudes.
Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
Green polygon in left panel highlights the over-density of blue, comoving stars identified by the search described in \sectionname~\ref{sec:data}.
Red line in right panel shows the zero-age main sequence of a $50~\textrm{Myr}$, $\feh = -1$ stellar population from the MIST isochrone library \citep{TODO}.
}
\label{fig:cmds}
\end{figure}

\todo{Left off here}

Figure \ref{fig_skypm} shows the spatial and proper motion distribution in the region of interest with the objects in
a small proper motion selection shown as black and red dots.  The color magnitude diagram (CMD) of the same objects
is shown in Figure \ref{fig_cmd} and clearly reveals a sequence of objects that follow the shape of a young main-sequence.
The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at fa distance of 25 kpc.  Finally, Figure \ref{fig_gass} shows a position-velocity diagram at the position of the cluster of the \citep[GASS;][]{McClure-Griffiths:2009} \hi data that has been Gaussian decomposed using the technique in \citet{Nidever:2008}.
The component of the LA II can be seen on the left-hand side of the figure and a similar \hie stream can be seen near the
position of the cluster.
% Yumi:
% Need a sentence or two for dust extinction correction somewhere in the above two paragraphs?

Isochrone: \citep{Fox:2018}

@@

>>>>

% typography
\setlength{\parindent}{1.\baselineskip}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\package}[1]{\textsl{#1}}
\newcommand{\gaia}{\textsl{Gaia}}
\newcommand{\pans}{\acronym{PS1}}
\newcommand{\decam}{DECam}
\newcommand{\DR}[1]{\acronym{DR#1}}
\newcommand{\todo}[1]{{\color{red} TODO: #1}}

@@

\section{Data} \label{sec:data}

\subsection{Cluster discovery with \gaia}
\label{sec:discovery}

@@

We then query all objects from the \gaia\ \DR{2} catalog within a polygon centered on the nominal position of the group (see above), with a width of $12^\circ$ and a height of $8^\circ$ in the Magellanic stream coordinate system \citep{Nidever:2008} (see Appendix~\ref{sec:queries} for the database query).
We cross-match the resulting catalog with \acronym{GALEX} \todo{citation} using a positional crossmatch requiring source separation $<2~\textrm{arcsec}$, and with \pans\ \todo{citation}\citep{Chambers:XX} using the cross-match provided by the \gaia\ science archive.
\figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram (left) and the \acronym{GALEX} NUV minus \pans\ $g$-band vs. \gaia\ \bprp\ color-color diagram (right) from the cross-matched photometry.
All magnitudes are corrected for dust extinction using the SFD \citep{Schlegel:1998} dust map.
The green polygon in the left panel of \figurename~\ref{fig:cmds} highlights the over-density of blue stars that were identified as comoving from the proper motion search described above.
The red line in right panel of \figurename~\ref{fig:cmds} is an isochrone (from MIST; \citealt{TODO}) for a $50~\textrm{Myr}$, $\feh = -1$ stellar population.

% Notebook: Figure-CMDs
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/gaia-galex-cmd.pdf}
\caption{Color-magnitude and color-color diagrams with \gaia\ ($G$, BP, RP), \acronym{GALEX} (NUV), and \pans\ ($g$) magnitudes.
Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
Green polygon in left panel highlights the over-density of blue, comoving stars identified by the search described in \sectionname~\ref{sec:discovery}.
Red line in right panel shows the zero-age main sequence of a $50~\textrm{Myr}$, $\feh = -1$ stellar population from the MIST isochrone library \citep{TODO}.
}
\label{fig:cmds}
\end{figure}

\subsection{Follow-up with \decam}
\label{sec:decam}

\todo{Nidever}

% Figure \ref{fig_skypm} shows the spatial and proper motion distribution in the region of interest with the objects in
% a small proper motion selection shown as black and red dots.  The color magnitude diagram (CMD) of the same objects
% is shown in Figure \ref{fig_cmd} and clearly reveals a sequence of objects that follow the shape of a young main-sequence.
% The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at fa distance of 25 kpc.  Finally, Figure \ref{fig_gass} shows a position-velocity diagram at the position of the cluster of the \citep[GASS;][]{McClure-Griffiths:2009} \hi data that has been Gaussian decomposed using the technique in \citet{Nidever:2008}.
% The component of the LA II can be seen on the left-hand side of the figure and a similar \hie stream can be seen near the
% position of the cluster.
% Yumi:
% Need a sentence or two for dust extinction correction somewhere in the above two paragraphs?

@@

\section{Proper motion cleaned}
\label{sec:pmclean}

\todo{APW}

\section{Stellar population characteristics}
\label{sec:popchars}

\todo{APW}

\section{Relation to HI gas}
\label{sec:higas}

\todo{Nidever}
